### 2022-07-16 response-letter.md

>*Lines 9-11: Please cite studies that have done this before! If there are no previous studies, it is important to highlight the novelty of your study.*

We have added more context in the introduction section, but we've found it hard
to expand the first paragraph. We believe that this particular paragraph needs
to be more succinct, at the same time that it provides a complete picture of the
paper, framed in a storytelling structure. Then, on the second paragraph, we
start providing literature background and many examples, to help the reader
understand where our paper stands in the scientific context. The references
suggested were indeed helpful; we have included Gotelli *et al*. (2010) in the
introduction (L. 28 & 33), Hurlbert and White (2005) (L. 14, 50 & 66), Hurlbert
and Jetz (2007) (L. 14 & 50), Ficetola *et al*. (2014) (L. 15 & 66); we have
also added Isaac, Mallet, and Mace (2004) (L.86), Rondinini *et al*. (2006) (L.
86), and Windsor *et al*. (2022) (L. 311 & 325). Finally, we have fixed the IUCN
reference, as pointed out by the reviewer in the annotated manuscript (L. 46),
and added citation regarding all software infrastructure used and availability
of our scripts (L. 158-165). Along with these references, we have included
discussions about the quality and accuracy of range maps (L. 46-58), examples of
data biases (L. 7-11), and we addressed the uniqueness of our study compared to
previous research (L. 13-18). We hope that this structure is clarifying and
appealing to the readers.

>*[...] I would add the need to provide more details on how you cleaned GBIF data before actually using it. You also need to provide many more details on data retrieval, which date range?*

Regarding the GBIF data cleaning, retrieval and the validation steps, we added a
more detailed description of our process (L. 144-165). Data
retrieving is detailed in the source code provided on our repository
(code/09-GBIF_data.jl). We used the list of species from the network dataset and
retrieved any occurrence within our bounding box (between longitudes -20.0 and
55.0 degrees; and latitudes -35.0 and 40.0 degrees). We changed two things
regarding geographical information during data retrieval:

1. We had originally added an argument to capture only the data that had
   information about the continent location equals to "AFRICA". However, this
   constrained our search by thousands of occurrences, and added a filtering
   layer that could be interpreted as "data cleaning". We removed that because
   we don't perform any kind of data cleaning with the IUCN dataset.

@@

>*Lines 124-131: I have a doubt about your data validation. First, you mentioned that you compiled point observation data from GBIF. Then you converted that data in the presence or absence of the focal taxon. How did you transform these data in the presence or absence once the GBIF provides just occurrence points (i.e. presence data)? This was not well explained. In general, absence data are not provided because the non-detection of a species in a location does not mean a true absence. This could just be a detection issue. Thus, it is needed to calculate the pseudo-absence data. Please explain this better in your manuscript.*

>*[...] the section on geographical data validation needs improvement, by explaining how you produced absence data from presence-only data base.*

For the validation step, we understand our phrasing was confusing, and we have
rewritten this section to clarify our method (L. 151-153). Rather than using
absence data, what we did was to transform the point data into raster files, and
then restrict our range maps to the locations where we had GBIF occurrences.
Therefore, the pixels where there are no GBIF occurrences are not considered
true absence of a species, but absence of **data** about the occurrence of that
species.

Finally, we have addressed all the other minor comments throughout the text as
detailed below:

- *Lines 68-70: This mismatch cannot just be a result of the overestimation of the predator’s range but it could be the result of misestimating both the predator's and prey's range. Please rephrase the sentence.*

  We've added citations in the Methods section to support our argument that a
  mismatch between ranges can be originated from different sources (L. 68-70).

- *L. 214-217 can be suppressed.*

  Agreed. We have suppressed lines 214-217.

- *PeerJ uses a structured abstract. I highly recommend authors to adhere to it when resubmitting the revised version.*

  The abstract is now restructured according to PeerJ guidelines.

- *Avoid citing tables and figures in the Discussion.*

  References to tables and figures in the Discussion section were suppressed,
  with the exception of Figure 05 (L. 305), which is an example of our results
  to clarify an important point of the discussion.

- *Lines 21-23: Are the cited literature examples of models that do not take ecological interactions into account? Use e.g. before.*

  The cited literature are not examples of models that do not take ecological
  interactions into account, but studies that have demonstrated how ecological
  interactions might be responsible for shaping a species' distribution. We've
  rewritten the sentence to clarify that.

- *Lines 68-70: This mismatch cannot just be a result of the overestimation of the predator’s range but it could be the result of misestimating both the predator's and prey's range. Please rephrase the sentence.*

  Lines 84-89: we have rewritten the sentence to include the consideration
  misestimation of both species in a trophic interaction. We have also added
  citations and examples.

- We have addressed the grammatical suggestions throughout the text, except for
  the legend of Figure 1. We thought that the suggested phrasing adds a little
  bit of confusion to the comprehension of the figure.

### 2022-07-16 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@40c766e52a0a7380952f78d649000b13025db880 🚀
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@6589da1782c0d676cd233e22335a24261ec0d2c3 🚀

We performed all analyses using \emph{Julia} v1.7.2 (Bezanson et al.
2017). We used the packages \texttt{SimpleSDMLayers.jl} (Dansereau and
Poisot 2021) to manipulate the raster layers,
\texttt{EcologicalNetworks.jl} (Poisot et al. 2019) to construct and
manipulate the interaction networks, and \texttt{GBIF.jl} (Dansereau and
Poisot 2021) to retrieve the species occurrences from GBIF. We also used
\emph{GDAL} (GDAL/OGR contributors 2021) to rasterize the IUCN range
maps (initially available as shapefiles from the Spatial Data Download
portal). All the scripts required to reproduce the analyses are
available at {[}\textbf{link to Zenodo archive}{]}.

@@

The proportion of GBIF pixels in updated ranges can only be equal to or
lower than that of the original ranges, as our analysis removes pixels
from the original range and does not add new ones. Rather, the absence
of a difference between the two types of ranges indicates that no pixels
with GBIF observations, hence likely true habitats, were removed by our
analysis. Here this proportion was mostly similar to that of the
original IUCN ranges for most predator species (fig.~\ref{fig:gbif}).
Two species showed no difference in proportion while four species showed
only small differences (\emph{Crocuta crocuta} lost 1.3\% of the
original data overlap; \emph{Acinonyx jubatus} lost 1.9\%;
\emph{Panthera pardus} lost 8.8\%; and \emph{Caracal caracal} lost
12.3\%). \textless!---\textgreater Note to self: here I calculated how
much the difference represents as a proportion of the total proportion,
which means the decreased rate. E.g., when the range\_prop\_diff is
equal to the original proportion (range\_prop), this means that this
species lost 100\% of the original proportion. Therefore I can't use
range\_prop\_diff numbers if I'm talking about \%
lost.\textless---\textgreater{} On the other hand, three species,
\emph{Canis aureus}, \emph{Canis mesomelas}, and \emph{Leptailurus
serval} showed very high differences, with overlaps lowered by 100\%,
57.4\%, and 100\% respectively. These last two species are also the only
predators with a single prey in our metaweb. \emph{Canis aureus} has
four preys, but it has one of the smallest ranges in IUCN, which is not
covered by any of its preys. This result reinforces the concern raised
in the literature on the use of IUCN range maps for species that are not
well known (Herkt, Skidmore, and Fahr 2017), demonstrating how small
range species are likely to have their distribution underestimated in
the IUCN database. Additionally, the fact that \emph{Canis aureus} had
such a conspicuous mismatch between both the original and updated IUCN
range maps, and between GBIF and IUCN data, may indicate a taxonomic
incongruency between the three databases used here, which we explore in
the Discussion section. Our results delineate how a mismatch between
GBIF and IUCN databases differ greatly with small changes in herbivore
species ranges, and it is somewhat positively related to range size for
predator species. Moreover, we show that accounting for interactions
does not necessarily aggravates this dissimilarity, but it is relevant
for species with little ecological information or specialists.

>>>>

We performed all analyses using \emph{Julia} v1.7.2 (Bezanson et al.
2017). We used the packages \texttt{SimpleSDMLayers.jl} (Dansereau and
Poisot 2021) to manipulate the raster layers,
\texttt{EcologicalNetworks.jl} (Poisot et al. 2019) to construct and
manipulate the interaction networks, and \texttt{GBIF.jl} (Dansereau and
Poisot 2021) to retrieve the species occurrences from GBIF. We also used
\emph{GDAL} (GDAL/OGR contributors 2021) to rasterize the IUCN range
maps (initially available as shapefiles from the Spatial Data Download
portal). All the scripts required to reproduce the analyses are
available at https://doi.org/10.5281/zenodo.6842861.

@@

The proportion of GBIF pixels in updated ranges can only be equal to or
lower than that of the original ranges, as our analysis removes pixels
from the original range and does not add new ones. Rather, the absence
of a difference between the two types of ranges indicates that no pixels
with GBIF observations, hence likely true habitats, were removed by our
analysis. Here this proportion was mostly similar to that of the
original IUCN ranges for most predator species (fig.~\ref{fig:gbif}).
Two species showed no difference in proportion while four species showed
only small differences (\emph{Crocuta crocuta} lost 1.3\% of the
original data overlap; \emph{Acinonyx jubatus} lost 1.9\%;
\emph{Panthera pardus} lost 8.8\%; and \emph{Caracal caracal} lost
12.3\%). On the other hand, three species, \emph{Canis aureus},
\emph{Canis mesomelas}, and \emph{Leptailurus serval} showed very high
differences, with overlaps lowered by 100\%, 57.4\%, and 100\%
respectively. These last two species are also the only predators with a
single prey in our metaweb. \emph{Canis aureus} has four preys, but it
has one of the smallest ranges in IUCN, which is not covered by any of
its preys. This result reinforces the concern raised in the literature
on the use of IUCN range maps for species that are not well known
(Herkt, Skidmore, and Fahr 2017), demonstrating how small range species
are likely to have their distribution underestimated in the IUCN
database. Additionally, the fact that \emph{Canis aureus} had such a
conspicuous mismatch between both the original and updated IUCN range
maps, and between GBIF and IUCN data, may indicate a taxonomic
incongruency between the three databases used here, which we explore in
the Discussion section. Our results delineate how a mismatch between
GBIF and IUCN databases differ greatly with small changes in herbivore
species ranges, and it is somewhat positively related to range size for
predator species. Moreover, we show that accounting for interactions
does not necessarily aggravates this dissimilarity, but it is relevant
for species with little ecological information or specialists.
